---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# checkdeps

<!-- badges: start -->
<!-- badges: end -->

The goal of checkdeps is to allow easily checking the versions of dependencies of a given package 
currently installed on the user's system, and eventually compare them with "reference" 
dependencies stored in a RData file. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lbusett/checkdeps")
```
## Example: checking currently installed versions of dependencies of an installed package:

```{r example}
library(checkdeps)
check_pkg_deps("ggplot2")
## basic example code
```

## Example: saving currently installed versions of dependencies of an installed package:

```{r example2}
library(checkdeps)
outfile <- tempfile(fileext = ".RData")
save_pkg_deps("ggplot2", outfile)
## basic example code
```

## Example: comparing currently installed versions of dependencies with those saved in a file:

```{r example3}
library(checkdeps)
prevfile <- outfile
compare_pkg_deps("ggplot2", prevfile)
## basic example code
```
